The Feasibility of Stylometry as a Service

### 2013-12-09 paper/paper.tex
Fixed some references.

Currently the JStylo and Anonymouth integrated open-source project
(JSAN) is available to download and can be installed on a machine that
runs the Java Virtual Machine (JVM).  While JSAN has been successfully
demonstrated to be effective in assisting authors with adversarial
stylometry \cite{journals/tissec/BrennanAG12}, the constraint of
downloading and installing the software on a machine powerful enough
to run machine learning algorithms on data sets, limits their
adoptability.  We propose increase the availability and usability of
JStylo and Anonymouth by offering them as a web service.

@@

A high latency system would not be well
suited for a web service.  An example high latency system could simply
entail sending an encrypted email to a third party who uses Anonymouth
locally and returns the encrypted result.  While this high-latency
system seems trivial, note that a naive implementation will reduce the
user's privacy.  For example, email is very subject to traffic
analysis (CITE) and encrypted email is easy to detect (CITE),
therefore this act alone would raise suspiction.  If this third party
was offering a high-latency anonymiziation service for numerous
people, the network graph would be easy to detect.

\subsection{Architecture Qualities}
There are several qualities of a system architecture that are
considers foundational (CITE lem bass).  These are: availability,
interoperability, modifiability, performance, security, testability,
and usability.  In additional we add privacy as an architecture
quality in our review.

Availability is the measure of the measure of the accesibility and
realibility of the system, e.g. how well does it handle errors.
Interoperability refers to the degree with which a system can interact
with its components or other systems.  Modifiability is important for
large systems so that they can be easily maintained and scale.  The
response of the system to input is its performance.  Security is the
review of a system's ability to protect sensitive data and prevent
unautorized and undesired behaviour.  Testability is an important
factor not only in development but also in a deployed system to ensure
that the system is working as designed.  Usability is notoriously bad
for security software (CITE How Johnny) and refers to the interaction
design.  Lastly, by privacy we mean how well a user's anonymitity is
protected.

@@

Man in the middle attacks: If a user accepts a rogue SSL certificate, it
may be possible to create a "man in the middle" attack where the user
believes he/she is communicating with a specific Stylometry Service,
but is infact communicating via an impersonated target.

Replay attacks: An evesdropper may 'replay' a message to the
webservice in an attempt to surrepituously revert parts of the text to
earlier versions. This may be possible as it is not documented whether
the current implementation uses nonces when transmitting messages.

HTML5 Canvas attacks: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented (see Contextis Browser Timing Attacks white paper) whereby
Firefox optimizations in the implementation of the
requestAnimationFrame method have been used by to detect differences
in link coloring across frames (allowing an adversary to determine if
a particular styometry service has been visited, for instance)

@@

>>>>

Currently the JStylo and Anonymouth integrated open-source project
(JSAN) \cite{BrennanG09}, \cite{journals/tissec/BrennanAG12},
\cite{conf/pet/McDonaldACSG12} is available to download and can be installed on a machine that
runs the Java Virtual Machine (JVM).  While JSAN has been successfully
demonstrated to be effective in assisting authors with adversarial
stylometry \cite{journals/tissec/BrennanAG12}, the constraint of
downloading and installing the software on a machine powerful enough
to run machine learning algorithms on data sets, limits their
adoptability.  We propose increase the availability and usability of
JStylo and Anonymouth by offering them as a web service.

@@

A high latency system would not be well suited for a web service.  An
example high latency system could simply entail sending an encrypted
email to a third party who uses Anonymouth locally and returns the
encrypted result.  While this high-latency system seems trivial, note
that a naive implementation will reduce the user's privacy.  For
example, email is very subject to traffic analysis
\cite{Mathewson04practicaltraffic} and encrypted email is easy to
detect, therefore this act alone would raise suspiction.  If
this third party was offering a high-latency anonymiziation service
for numerous people, the network graph would be easy to detect.

\subsection{Architecture Qualities}
There are several qualities of a system architecture that are
considers foundational\cite{Bass:2012:SAP:2392670}.  These are: availability,
interoperability, modifiability, performance, security, testability,
and usability.  In additional we add privacy as an architecture
quality in our review.

Availability is the measure of the measure of the accesibility and
realibility of the system, e.g. how well does it handle errors.
Interoperability refers to the degree with which a system can interact
with its components or other systems.  Modifiability is important for
large systems so that they can be easily maintained and scale.  The
response of the system to input is its performance.  Security is the
review of a system's ability to protect sensitive data and prevent
unautorized and undesired behaviour.  Testability is an important
factor not only in development but also in a deployed system to ensure
that the system is working as designed.  Usability is notoriously bad
for security software \cite{Whitten:1999:WJC:1251421.1251435} and
refers to the interaction design.  Lastly, by privacy we mean how well
a user's anonymitity is protected.

@@

{\bf Man in the middle attacks}: If a user accepts a rogue SSL certificate, it
may be possible to create a "man in the middle" attack where the user
believes he/she is communicating with a specific Stylometry Service,
but is infact communicating via an impersonated target.

{\bf Replay attacks}: An evesdropper may 'replay' a message to the
webservice in an attempt to surrepituously revert parts of the text to
earlier versions. This may be possible as it is not documented whether
the current implementation uses nonces when transmitting messages.

{\bf HTML5 Canvas attacks}: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented \cite{BrowserTiming} whereby Firefox optimizations
in the implementation of the requestAnimationFrame method have been
used by to detect differences in link coloring across frames (allowing
an adversary to determine if a particular styometry service has been
visited, for instance)

@@

\section{Evaluation of Architecture Qualities}

\subsection{Performance.}

\subsection{Testability.}
